InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex

>>>>

We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
